Draft

### 2024-08-13 All_param.Rmd
Ready to knit I hope

    colnames(df_b) <- paste0(raw_names, ".MC", b)[-(11:14)]
    from_local <- function(j){sum(df_b[2+j] /p)} # (nb_var+2)*(b-1)
    est_b <- data.frame(from_local(1), from_local(2), from_local(3), from_local(4), from_local(5), from_local(6), from_local(7), from_local(8), 
                        (from_local(5))/(from_local(1)), (from_local(6))/(from_local(2)), 
                        (from_local(7))/(from_local(3)), (from_local(8))/(from_local(4)))
    nb_est <- length(est_b) # number of estimations
    rownames(est_b) <- paste0("ech", b)
    colnames(est_b) <- paste0("est_", b)

@@

    BOOT_var[[b]] <- as.data.frame(mapply(var, est_boot_val))
    names(BOOT_var)[b] <- paste("Variance", b, sep = "")
    BOOT_df <- c(BOOT_df, list(data_init = df_b, data_boot = df_boot))
    names(BOOT_df)[(2*b-1):(2*b)] <- c(paste("df_MC", b, sep = ""), paste("df_boot", b, sep = ""))
    BOOT_est <- c(BOOT_est, list(est_init_b = est_b, est_boot_b = est_boot_val))
    names(BOOT_est)[(2*b-1):(2*b)] <- c(paste("est_MC", b, sep = ""), paste("est_boot", b, sep = ""))

    # Confidence intervals
    norm_CI <- data.frame(useless = rep(0, 2))
    perc_CI <- data.frame(useless = rep(0, 2))
    rev_perc_CI <- data.frame(useless = rep(0, 2))
    for (l in 1:length(est_boot_val)) { # Loop: one estimator each time
      sorted_est <- sort(est_boot_val[,l])
      lim_inf <- sorted_est[floor(B2*2.5/100)]
      lim_sup <- sorted_est[B2 - floor(B2*2.5/100)]
      perc_CI <- cbind(perc_CI, data.frame(c(lim_inf, lim_sup)))
      rev_perc_CI <- cbind(rev_perc_CI, data.frame(c(as.numeric(est_b[l])*2 - lim_sup, as.numeric(est_b[l])*2 - lim_inf)))
      norm_CI <- cbind(norm_CI, data.frame(c(as.numeric(est_b[l])-qnorm(0.975)*sqrt(var(est_boot_val[,l])), as.numeric(est_b[l])+qnorm(0.975)*sqrt(var(est_boot_val[,l])))))
    }
    norm_CI$useless <- NULL
    perc_CI$useless <- NULL
    rev_perc_CI$useless <- NULL
    nam_lim <- paste0("lim_", raw_names)[-(1:2)]
    colnames(norm_CI) <- nam_lim
    colnames(perc_CI) <- nam_lim
    colnames(rev_perc_CI) <- nam_lim
    BCa_CI <- bcanon(df_b, est_b, est_boot_val, p, nb_var)
    colnames(BCa_CI) <- nam_lim
    all_CI <- list(Normal = as.data.frame(norm_CI), Percentile = as.data.frame(perc_CI), `Reverse percentile` = as.data.frame(rev_perc_CI), BCa = as.data.frame(BCa_CI))
    BOOT_CI[[b]] <- all_CI
    names(BOOT_CI)[b] <- paste0("CI", b)
  }
  return(list(`Local Variables` = BOOT_df, Estimations = BOOT_est, Variances = BOOT_var, `Confidence Intervals` = BOOT_CI))
  # Local Variables: local variables (number and volume) for each point in each sample
  # Estimations: 3 estimations (number, volume, ratio volume / number) for each sample
  # Variances: mean of the bootstrap variance for each estimator
  # Confidence Intervals: 3 different forms of 95% confidence intervals, for each total / ratio
}
```

@@

```{r}
# We want all the variances obtained for each parameter of interest, 
# to find the mean for each of these series
EST_nb <- c()
EST_vol <- c()
EST_ratio <- c()
for (elt in res2$Estimations) {
  if ( nrow(elt) != 1){ # we target bootstrap samples made from each MC iteration
    EST_nb <- append(EST_nb, mean(elt$est_nb))
    EST_vol <- append(EST_vol, mean(elt$est_vol))
    EST_ratio <- append(EST_ratio, mean(elt$est_ratio))
  }
}
```

```{r}
cat("Mean of the means of estimations obtained through each bootstrap process:\n - for the number of trees:", mean(EST_nb), "\n - for the volume of trees:", mean(EST_vol), "\n - for the ratio volume / number of trees:", mean(EST_ratio))

@@

```{r}
# We want all the variances obtained for each parameter of interest, 
# to find the mean for each of these series
VAR_nb <- c()
VAR_vol <- c()
VAR_ratio <- c()
for (elt in res2$Variances) {
  VAR_nb <- append(VAR_nb, elt$var_nb)
  VAR_vol <- append(VAR_vol, elt$var_vol)
  VAR_ratio <- append(VAR_ratio, elt$var_ratio)
}
```

```{r}
cat("Mean of the variance of bootstrap samples:\n - for the number of trees:", mean(VAR_nb), "\n - for the volume of trees:", mean(VAR_vol), "\n - for the ratio volume / number of trees:", mean(VAR_ratio))

@@

```{r eval=FALSE, include=FALSE}
### DRAFT

  # Coverage rate
  TC_nb <- (1/nrow(CI_nb))*sum( mapply(function(a,b){as.numeric((29272 > a) & (29272 < b))}, CI_nb[1], CI_nb[2]) )
  TC_vol <- (1/nrow(CI_vol))*sum( mapply(function(a,b){as.numeric((5412.722 > a) & (5412.722 < b))}, CI_vol[1], CI_vol[2]) )
  TC_ratio <- (1/nrow(CI_ratio))*sum( mapply(function(a,b){as.numeric((0.1849112 > a) & (0.1849112 < b))}, CI_ratio[1], CI_ratio[2]) )

  # Lower tail
  low_tail_nb <- (1/nrow(CI_nb))*sum( mapply(function(a){as.numeric(29272 < a)}, CI_nb[1]) )
  low_tail_vol <- (1/nrow(CI_vol))*sum( mapply(function(a){as.numeric(5412.722 < a)}, CI_vol[1]) )
  low_tail_ratio <- (1/nrow(CI_ratio))*sum( mapply(function(a){as.numeric(0.1849112 < a)}, CI_ratio[1]) )

  # Upper tail
  up_tail_nb <- (1/nrow(CI_nb))*sum( mapply(function(b){as.numeric(29272 > b)}, CI_nb[2]) )
  up_tail_vol <- (1/nrow(CI_vol))*sum( mapply(function(b){as.numeric(5412.722 > b)}, CI_vol[2]) )
  up_tail_ratio <- (1/nrow(CI_ratio))*sum( mapply(function(b){as.numeric(0.1849112 > b)}, CI_ratio[2]) )

  # Mean length of CIs
  length_nb <- mean( mapply(function(a,b){b-a}, CI_nb[1], CI_nb[2]) )
  length_vol <- mean( mapply(function(a,b){b-a}, CI_vol[1], CI_vol[2]) )
  length_ratio <- mean( mapply(function(a,b){b-a}, CI_ratio[1], CI_ratio[2]) )

  df_TC <- data.frame(TC = c(TC_nb, TC_vol, TC_ratio), Upper = c(low_tail_nb, low_tail_vol, low_tail_ratio), Lower = c(up_tail_nb, up_tail_vol, up_tail_ratio), Mean_length = c(length_nb, length_vol, length_ratio))
```

@@

```{r}
diff_percent <- function(x,y){100*(max(res1$Variances[x],mean(y))-min(res1$Variances[x],mean(y)))/min(res1$Variances[x],mean(y))}
cat("Difference between the two estimations of variance: \n - for the number of trees: ", diff_percent(1, VAR_nb), "%", "\n - for the volume of trees: ", diff_percent(2, VAR_vol), "%\n - for the ratio volume / number of trees: ", diff_percent(3, VAR_ratio), "%", sep = "")

>>>>

    colnames(df_b) <- paste0(raw_names, ".MC", b)[-(11:14)]
    from_local <- function(j){sum(df_b[2+j] /p)} # (nb_var+2)*(b-1)
    est_b <- data.frame(from_local(1), from_local(2), from_local(3), from_local(4), from_local(5), from_local(6), from_local(7), from_local(8), 
                        (from_local(5))/(from_local(1)), (from_local(6))/(from_local(2)), 
                        (from_local(7))/(from_local(3)), (from_local(8))/(from_local(4)))
    nb_est <- length(est_b) # number of estimations
    colnames(est_b) <- paste0("est_", raw_names)[-(1:2)]

@@

    BOOT_var[[b]] <- as.data.frame(t(mapply(var, est_boot_val)))
    colnames(BOOT_var[[b]]) <- paste0("var_", raw_names)[-(1:2)]
    names(BOOT_var)[b] <- paste("Variance", b, sep = "")
    BOOT_df <- c(BOOT_df, list(data_init = df_b, data_boot = df_boot))
    names(BOOT_df)[(2*b-1):(2*b)] <- c(paste("df_MC", b, sep = ""), paste("df_boot", b, sep = ""))
    BOOT_est <- c(BOOT_est, list(est_init_b = est_b, est_boot_b = est_boot_val))
    names(BOOT_est)[(2*b-1):(2*b)] <- c(paste("est_MC", b, sep = ""), paste("est_boot", b, sep = ""))

    # Confidence intervals
    norm_CI <- data.frame(matrix(numeric(0), nrow = 2))
    perc_CI <- data.frame(matrix(numeric(0), nrow = 2))
    rev_perc_CI <- data.frame(matrix(numeric(0), nrow = 2))
    # norm_CI <- data.frame(useless = rep(0, 2))
    # perc_CI <- data.frame(useless = rep(0, 2))
    # rev_perc_CI <- data.frame(useless = rep(0, 2))
    for (l in 1:length(est_boot_val)) { # Loop: one estimator each time
      sorted_est <- sort(est_boot_val[,l])
      lim_inf <- sorted_est[floor(B2*2.5/100)]
      lim_sup <- sorted_est[B2 - floor(B2*2.5/100)]
      perc_CI <- cbind(perc_CI, data.frame(c(lim_inf, lim_sup)))
      rev_perc_CI <- cbind(rev_perc_CI, data.frame(c(as.numeric(est_b[l])*2 - lim_sup, as.numeric(est_b[l])*2 - lim_inf)))
      norm_CI <- cbind(norm_CI, data.frame(c(as.numeric(est_b[l])-qnorm(0.975)*sqrt(var(est_boot_val[,l])), as.numeric(est_b[l])+qnorm(0.975)*sqrt(var(est_boot_val[,l])))))
    }
    # norm_CI$useless <- NULL
    # perc_CI$useless <- NULL
    # rev_perc_CI$useless <- NULL
    nam_lim <- paste0("lim_", raw_names)[-(1:2)]
    colnames(norm_CI) <- nam_lim
    colnames(perc_CI) <- nam_lim
    colnames(rev_perc_CI) <- nam_lim
    BCa_CI <- bcanon(df_b, est_b, est_boot_val, p, nb_var)
    colnames(BCa_CI) <- nam_lim
    all_CI <- list(Normal = as.data.frame(norm_CI), Percentile = as.data.frame(perc_CI), `Reverse percentile` = as.data.frame(rev_perc_CI), BCa = as.data.frame(BCa_CI))
    BOOT_CI[[b]] <- all_CI
    names(BOOT_CI)[b] <- paste0("CI", b)
  }
  return(list(`Local Variables` = BOOT_df, Estimations = BOOT_est, Variances = BOOT_var, `Confidence Intervals` = BOOT_CI))
  # Local Variables: local variables (number and volume) for each point in each sample
  # Estimations: 3 estimations (number, volume, ratio volume / number) for each sample
  # Variances: mean of the bootstrap variance for each estimator
  # Confidence Intervals: 3 different forms of 95% confidence intervals, for each total / ratio
}
```

@@

```{r}
# We want all the variances obtained for each parameter of interest, 
# to find the mean for each of these series
raw_names <- c("x", "y", "nb", "nb_s","nb_m", "nb_b", "vol", "vol_s", "vol_m", "vol_b", "ratio", "ratio_s", "ratio_m", "ratio_b")
EST_names <- paste0("EST_", raw_names)[-(1:2)]
# est_names <- paste0("est_", raw_names)[-(1:2)]

for (j in EST_names) {
  assign(j, data.frame(matrix( numeric(0), nrow = (length(res2$Estimations)/2) )))
}

for (elt in res2$Estimations) {
  if ( nrow(elt) != 1 ){ # we target bootstrap samples made from each MC iteration
    for (j in 1:length(EST_names)) { # For each estimation
      x <- append(get(x = EST_names[j]), mean(unlist(elt[j])))
      assign(EST_names[j], x)
    }
  }
}
```

```{r}
cat("Mean of the means of estimations obtained through each bootstrap process:\n - for the number of trees:", mean(unlist(EST_nb)), "\n - for the volume of trees:", mean(unlist(EST_vol)), "\n - for the ratio volume / number of trees:", mean(unlist(EST_ratio)),
        "\n\n - for the number of small trees:", mean(unlist(EST_nb_s)), "\n - for the volume of small trees:", mean(unlist(EST_vol_s)), "\n - for the ratio volume / number of trees:", mean(unlist(EST_ratio_s)),
    "\n\n - for the number of medium trees:", mean(unlist(EST_nb_m)), "\n - for the volume of medium trees:", mean(unlist(EST_vol_m)), "\n - for the ratio volume / number of trees:", mean(unlist(EST_ratio_m)),
    "\n\n - for the number of big trees:", mean(unlist(EST_nb_b)), "\n - for the volume of big trees:", mean(unlist(EST_vol_b)), "\n - for the ratio volume / number of trees:", mean(unlist(EST_ratio_b)))

@@

```{r}
# We want all the variances obtained for each parameter of interest, 
# to find the mean for each of these series
VAR_names <- paste0("VAR_", raw_names)[-(1:2)]

for (j in VAR_names) {
  assign(j, data.frame(matrix( numeric(0), nrow = (length(res2$Estimations)/2) )))
}

for (elt in res2$Variances) {
  for (j in 1:length(VAR_names)) { # For each estimation
    x <- append(get(x = VAR_names[j]), mean(unlist(elt[j])))
    assign(VAR_names[j], x)
  }
}
```

```{r}
cat("Mean of the variance of bootstrap samples:\n - for the number of trees:", mean(unlist(VAR_nb)), "\n - for the volume of trees:", mean(unlist(VAR_vol)), "\n - for the ratio volume / number of trees:", mean(unlist(VAR_ratio)),
        "\n\n - for the number of small trees:", mean(unlist(VAR_nb_s)), "\n - for the volume of small trees:", mean(unlist(VAR_vol_s)), "\n - for the ratio volume / number of trees:", mean(unlist(VAR_ratio_s)),
    "\n\n - for the number of medium trees:", mean(unlist(VAR_nb_m)), "\n - for the volume of medium trees:", mean(unlist(VAR_vol_m)), "\n - for the ratio volume / number of trees:", mean(unlist(VAR_ratio_m)),
    "\n\n - for the number of big trees:", mean(unlist(VAR_nb_b)), "\n - for the volume of big trees:", mean(unlist(VAR_vol_b)), "\n - for the ratio volume / number of trees:", mean(unlist(VAR_ratio_b)))

@@

@@

```{r}
diff_percent <- function(x,y){100*(max(res1$Variances[x],mean(unlist(y)))-min(res1$Variances[x],mean(unlist(y))))/min(res1$Variances[x],mean(unlist(y)))}
cat("Difference between the two estimations of variance: \n - for the number of trees: ", diff_percent(1, VAR_nb), "%", "\n - for the volume of trees: ", diff_percent(5, VAR_vol), "%\n - for the ratio volume / number of trees: ", diff_percent(9, VAR_ratio), "%", 
    "\n\n - for the number of small trees:", diff_percent(2, VAR_nb_s), "%", "\n - for the volume of small trees:", diff_percent(6, VAR_vol_s), "%", "\n - for the ratio volume / number of trees:", diff_percent(10, VAR_ratio_s), "%",
    "\n\n - for the number of medium trees:", diff_percent(3, VAR_nb_m), "%", "\n - for the volume of medium trees:", diff_percent(7, VAR_vol_m), "%", "\n - for the ratio volume / number of trees:", diff_percent(11, VAR_ratio_m), "%",
    "\n\n - for the number of big trees:", diff_percent(4, VAR_nb_b), "%", "\n - for the volume of big trees:", diff_percent(8, VAR_vol_b), "%", "\n - for the ratio volume / number of trees:", diff_percent(12, VAR_ratio_b), "%",
    sep = "")

### 2024-08-13 Draft/Draft.Rmd
Ready to knit I hope

>>>>

##### From All_param -----------

```{r eval=FALSE, include=FALSE}
### DRAFT

  # Coverage rate
  TC_nb <- (1/nrow(CI_nb))*sum( mapply(function(a,b){as.numeric((29272 > a) & (29272 < b))}, CI_nb[1], CI_nb[2]) )
  TC_vol <- (1/nrow(CI_vol))*sum( mapply(function(a,b){as.numeric((5412.722 > a) & (5412.722 < b))}, CI_vol[1], CI_vol[2]) )
  TC_ratio <- (1/nrow(CI_ratio))*sum( mapply(function(a,b){as.numeric((0.1849112 > a) & (0.1849112 < b))}, CI_ratio[1], CI_ratio[2]) )

  # Lower tail
  low_tail_nb <- (1/nrow(CI_nb))*sum( mapply(function(a){as.numeric(29272 < a)}, CI_nb[1]) )
  low_tail_vol <- (1/nrow(CI_vol))*sum( mapply(function(a){as.numeric(5412.722 < a)}, CI_vol[1]) )
  low_tail_ratio <- (1/nrow(CI_ratio))*sum( mapply(function(a){as.numeric(0.1849112 < a)}, CI_ratio[1]) )

  # Upper tail
  up_tail_nb <- (1/nrow(CI_nb))*sum( mapply(function(b){as.numeric(29272 > b)}, CI_nb[2]) )
  up_tail_vol <- (1/nrow(CI_vol))*sum( mapply(function(b){as.numeric(5412.722 > b)}, CI_vol[2]) )
  up_tail_ratio <- (1/nrow(CI_ratio))*sum( mapply(function(b){as.numeric(0.1849112 > b)}, CI_ratio[2]) )

  # Mean length of CIs
  length_nb <- mean( mapply(function(a,b){b-a}, CI_nb[1], CI_nb[2]) )
  length_vol <- mean( mapply(function(a,b){b-a}, CI_vol[1], CI_vol[2]) )
  length_ratio <- mean( mapply(function(a,b){b-a}, CI_ratio[1], CI_ratio[2]) )

  df_TC <- data.frame(TC = c(TC_nb, TC_vol, TC_ratio), Upper = c(low_tail_nb, low_tail_vol, low_tail_ratio), Lower = c(up_tail_nb, up_tail_vol, up_tail_ratio), Mean_length = c(length_nb, length_vol, length_ratio))
```
